---
title: "Data Science Online Exam"
output: html_notebook
---

# 1. Write a R code to Generate 6x6 matrix (A) using the random numbers between 1 to 100 & generate anther 6x6 (b) using random numbers between 500 to 600

 a. Find the range of matrices A and B.
 b. Find the max value from each row of the matrices A and B.
 c. Find the diagonal values of matrices A&B.
 d. Multiply matrices A and B
 e Replace the 4th row of Matrix A with diagonal values of matrix B
 f. Multiply matrices A & B and store the values on X.
 g. Divide the matrix A with matrix B.

```{r}
# 1). Write a program to generate 6*6 matrix (A) using a random number between 1 to 100 and another one (B) from 500 to 600
a <- matrix(sample(1:100, 36), 6, 6)
b <- matrix(sample(500:600, 36), 6, 6)

```
```{r}
# b). Find max value from each row of A and B
aMaxRow <- apply(a, 1, max)
bMaxRow <- apply(b, 1, max)

```
```{r}
# d). Multiply matrices A and B
a %*% b
```

```{r}
# e). Replace the 4th row of matrix A with diagonal value of matrix B
a[4, ] <- diag(t(b))
```

```{r}
# f). Multiply matrix A & B and store value in x
x <- a %*% b
```


```{r}
# e). divide matrix A & B
a / b
```

#2. Create a table using dataframe/tibble with the following categories(a to f) 
 
a First name,
b. Second Name,
c. Age,
d. Occupation,
e. Place,
f. Random numbers( between 1 to 10)

And input at least 10 samples(observation) and do the following
 g. Extract the last column (f)
 h. Find the sum, mean and length of the extracted column
 
```{r}
 # a).First name

first_name = c("Pel", "Chea", "Pong", "Khean", "Thon", "Ly", "Houerng", "Sun", "Daro", "Ty")


``` 


```{r}
# b).Second name

second_name = c("Dane", "Nataly", "Channy", "Sreythou", "Lyana", "Chandara", "Hen", "Jenny", "Dalya", "Leapheng")

```

```{r}
# c). Age
age = c(21, 21, 23, 21, 20, 24, 21, 21, 21, 20)

```

```{r}
# d). Occupation 
occupation = c("Shop owner", "Engineering", "Teacher", "Singer", "Engineering", "Shop owner", "Teacher", "Business Advisor", "Trip Advisor", "Shop owner")

```

```{r}
# e). Place
place = c("Takeo", "Siem Reap", "Phnom Penh", "Phnom Penh", "Siem Reap", "Banteay Meanchey", "Kirirom", "Phnom Penh", "Kirirom", "Phnom Penh")

```

```{r}
# f). random number (between 1 to 10)
random = sample(1:10)

data_table <- data.frame(First_Name = first_name, Second_Name=second_name, Age = age, Occupation = occupation, Place = place, Random_Number = random)
data_table

```


```{r}
# g). Extract the las column (F)
random_col <- data_table$Random.Number
random_col

```


```{r}
# h). find the sum, mean and length of the extracted column
sum <- sum(random_col)
sum

mean <- mean(random_col)
mean

length <- length(random_col)
length
```

# 3. Create a.txt file (Minimun : 150 words) with the latest news(In English) in cambodia from the official news agency's website (Note: Include the reference link) and do the following

 a. Read the .txt file
 b. Perform the Tokenization & count the words
 c. Identify the most repeated word and replace that word with “KIT”
 d. Perform the Sentiment analysis
 e. Plot the graph between “words count” and “words” using geom_col()

e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color, Center, space between graph and title = 20.
	e.2. Y-axis title =“List of words”, Size=10, Bold, Text in Red color, Center, space between graph and title = 20.
	e.3. Graph title =”Text Mining using R”,Size = 25, Bold, Center, Text in Yellow color, space between graph and title = 25.



 
```{r}
library(tokenizers)
#a. Read the .txt file
# text is from https://www.phnompenhpost.com/business/virtual-reality-tech-catching-eyes-local-businesses
data <- read.delim("D:/Lecture/semester VII/Data Science/R/phnompenhpost.txt")
data

#b. Perform the Tokenization count the words
words_data <- paste(data)
tokens <- tokenize_words(words_data)
count <- count_words(words_data)
count

#c. Identify the most repeated word and replace that word with “KIT”
#Identify the most repeated word
most_words <- names(table(tokens))[as.vector(table(tokens))==max(table(tokens))]
most_words_count <- max(table(tokens))
print("The Most repeated word are: ")
most_words
print("Repeated for:  ")
most_words_count

#replace that word with “KIT”
subs <- gsub(most_words, "KIT", tokens)
subs

```




#4. Find the assigned Dataset from the list below and perform the following (20 Marks)
a. Import and Clean the dataset.
b. Find the x and y variables(axis) from the assigned dataset and give the reason for
selecting the x and y axis.
c. Plot the graph using geom_col() and perform the linear model in statistics.
d. Perform the facet with the available columns(Choose the any two variables from the
columns)
e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis &amp;
graph)
e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space
between graph and title = 20.
e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space
between graph and title = 20.
e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space
between graph and title = 25.


```{r}
# a. Import and Clean the dataset.
library("tidyverse")
dataset = read_csv("D:/Lecture/semester VII/Data Science/R/movies.csv")
dataset
#is.na(dataset)
# the dataset is already clean there is no NA so no need to clean again.

# b. Find the x and y variables(axis) from the assigned dataset and give the reason for
# selecting Budget as X and Year as Y so we can view each year in the column graph that may easy to understand.
plot <- ggplot(dataset, aes(x=budget, y=year)) + 
    xlab("Budget") +
    ylab("Year")

# c. Plot the graph using geom_col() and perform the linear model in statistics.
# using geom_col
plot <- plot+geom_col()

#perform linear model
plot <- plot+geom_smooth(method="lm")
plot

# d. Perform the facet with the available columns(Choose the any two variables from the columns)
# use facet with 2 variable by the year budget and domgross
plot+facet_grid(domgross~year)

# use facet with 1 variable by the year of budget
plot <- plot+facet_wrap(~year)
plot

# e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis graph)
#e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space between graph and title = 20.
#e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space between graph and title = 20.
#e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space between graph and title = 25.
plot <- plot +
  ggtitle("Budget") + theme(
  axis.title.x=element_text(size=10, color="green", face="bold", margin=margin(t=20,r=20,b=0,l=0)),
  axis.title.y=element_text(size=10, color="yellow", face="bold", margin=margin(t=0,r=20,b=0,l=20)),
  plot.title=element_text(size=25, color="blue", face="bold", margin=margin(t=25,r=0,b=25,l=0))
  )
plot
```


 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
